### 2017-07-29 README.Rmd
added nloptr to depends. minor readme updates

> Doubly Robust, Asymptotically Linear Targeted Minimum Loss-Based Estimation

@@

`drtmle` is an R package that computes marginal effect estimators for binary 
treatments on continuous and binary outcomes. The TMLE estimators are doubly
robust, not only with respect to consistency, but also with respect to asymptotic 
normality, as discussed in Benkeser, Carone, van der Laan \& Gilbert, 2017,(_accepted Biometrika_, [working paper](http://biostats.bepress.com/ucbbiostat/paper356/)).

>>>>

> Nonparametric estimators of the average treatment effect with doubly-robust confidence intervals and hypothesis tests

@@

`drtmle` is an R package that computes marginal effect estimators for binary 
treatments on continuous and binary outcomes. The targeted minimum loss-based (TMLE) estimators are doubly robust, not only with respect to consistency, but also with respect to asymptotic normality, as discussed in Benkeser, Carone, van der Laan \& Gilbert, 2017,(_accepted Biometrika_, [working paper](http://biostats.bepress.com/ucbbiostat/paper356/)). Therefore, it is possible to construct doubly-robust confidence intervals and hypothesis tests. Also included are methods for computing valid confidence intervals for an inverse probability of treatment weighted (IPTW) estimator of the average treatment effect when the propensity score is estimated via super learning, as discussed in [van der Laan, 2014](https://www.degruyter.com/downloadpdf/j/ijb.2014.10.issue-1/ijb-2012-0038/ijb-2012-0038.pdf).
